### 2014-10-28 Draft/evaluation.tex
included formal def

\subsection{Experimental Setup.} 
We first manually annotated the sentences in the API documents of the two APIs.
Two authors manually labeled each sentence in the API documentation as sentence containing 
temporal constraints or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently. 
We use these classified sentences as the golden set for calculating precision and recall.

@@

%We next describe our evaluation results.

@@

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method.
\tool, thus incorrectly identifies the sentence as a constraint sentence.

@@

If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our proposed framework.
In the future, we plan to investigate techniques to construct better domain dictionaries for software API.

@@

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluations are representative of true practice. To minimize the threat, we used API documents of two different API's: JDK \CodeIn{java.io} and \amazon. On one hand, Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages. In contrast, \amazon\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Furthermore, the difference in the functionalities provided by the two API's also address the issue of over fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects API's.

>>>>

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the two APIs.
Two authors manually labeled each sentence in the API documentation as sentence containing 
temporal constraints or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently. 
We use these classified sentences as the golden set for calculating precision and recall.

@@

We next present our evaluation results.

@@

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
However \tool\ fails to make the distinction that it happens internally (enforced in the body) in the method.
\tool, thus incorrectly identifies the sentence as a constraint sentence.

@@

If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our approach.
In the future, we plan to investigate techniques to construct better domain dictionaries for software API.

@@

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice. To minimize the threat, we used API documents of two different API's: JDK \CodeIn{java.io} and \amazon. On one hand, Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages. In contrast, \amazon\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Furthermore, the difference in the functionalities provided by the two API's also address the issue of over fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects API's.
